Continuous voting by approval and participation

### 2015-04-24 ApresentacoesArtigos/collectiveRanking/paper.tex
arrumada autoria
added about bonds

\author{Renato Fabbri\affil{2}{University of S\~ao Paulo}
\and
Ricardo Poppi\affil{1}{Brazilian General Secretariat of the Republic}
}
%James Smith\affil{2}{University of Oregon}
%\and
%Jane Smith\affil{1}{}
%}

@@

>>>>

%\author{Renato Fabbri\affil{2}{University of S\~ao Paulo}
\author{Renato Fabbri\affil{2}{University of S\~ao Paulo}
\and
Ricardo Poppi\affil{1}{Brazilian Presidency of the Republic}
}
%James Smith\affil{2}{University of Oregon}
%\and
%Jane Smith\affil{1}{}
%}

@@

Thresholds might be dependent on proposal, such as given by coherent relations. Immediate examples are: $\overline{\gamma_i}=1-\frac{\eta_i}{max(\{\eta_j , \forall j \})}$ or $\overline{\alpha_i} = 1-\gamma_i$. These bonds among proposal variables has been discarded by the staff in present initial steps.
